From Classification to Naming:\\ Modeling Entry-level Names for Objects in Images

### 2020-02-05 papers/ACL2020/experiments_merged.tex

\paragraph{Data}
We split \mn into training ($21K$~objects) and test data ($1,072$), where the test data corresponds to the overlap of \mn (MN) and the \vg (VG) test split used by  \newcite{anderson2018updown}. 
The target vocabulary of the test data is MN442: the 442 entry-level names we derived from \mn. %the overlap of MN442 and VG ($355$ names). 
For transfer learning we train models on the ground truth entry-level names provided by \mn, and compare this to training on \vg labels.

@@

\begin{itemize}
\item FRCNN$_{\text{VG1600}}$: This is \citep{anderson2018updown}'s model\footnote{We used the code and model available at  \url{github.com/peteanderson80/bottom-up-attention}. The model is trained with an additional output over attributes, but we only use the object class prediction layer.} that is optimized for a set of 1600 object names in \vg. This set was obtained by first taking the 2500 most frequent names in \vg and then (manually) filtering certain names.
 \item  FRCNN$_{\text{MN442}}$: we pre-process the \vg data as in \citeauthor{anderson2018updown}, but restrict the object classes to the $442$~entry-level names found in \mn (Section~\ref{sect:mn_analysis}). 
For training, we use a PyTorch reimplementation of Faster. R-CNN\footnote{\url{github.com/jwyang/faster-rcnn.pytorch}}
\end{itemize}

The two former models are trained on \vg, which has almost 4 million labeled objects.
\mn is too small to train object detection models on it from scratch, which requires learning millions of parameters.
On the other hand, obtaining enough naming data to be able to estimate entry-level names for larger datasets is very costly and probably unrealistic.
Therefore, we investigate the possibility of obtaining effective entry-level naming models via transfer learning, fine-tuning existing models with \mn data.
We do so with the standard methodology of taking the last hidden layer of existing Computer Vision models as input, and train object classification models to predict entry-level names (MN442).

We experiment with two kinds of input features, as well as different training vocabularies and ground-truth names for instances, similar to the detection models above.
This yields the following 4 transfer-learning-based naming models:
\begin{itemize}
\item FRCNN$_{\text{VG1600--VGMN}}$:
	This model extracts features from the object classification model FRCNN$_{\text{VG1600}}$\footnote{
	As experimental results will show, FRCNN$_{\text{VG1600}}$ is more effective than FRCNN$_{\text{MN442}}$, so we only use the former.
}. We expect these to be very good features for our task, as they have been obtained with the same task (object classification) and dataset (\vg).  For each object (i.e.,~bounding box) in \mn, we extract its activation features from FRCNN's last hidden layer before the output layer. The model uses the VGMN vocabulary (overlap of the full ManyNames vocabulary with VG).
  \item ResNet-VGMN: 
For comparison, we consider a much less informed input, namely the features from the ResNet-101 image classification model, that was used to initialize the FRCNN models above, and pretrained on ImageNet \cite{imagenet_cvpr09}. 
Results should of course be worse, and our aim is to assess the feasibility of using such generic object representations to obtain entry-level names. ResNet-VGMN uses the VGMN vocabulary; we trained two models, optimized on VG and MN ground truth names, respectively, but report only the one optized on VG (the other one yielded similar output).
 \item  ResNet-MN442 (two models):
 The same model as ResNet-VGMN, but trained with a vocabulary of 442 entry-level names; we optimized for on VG or MN ground truth names respectively.
\end{itemize}
Note that these four models are optimized on the $21$K~objects in \mn. 
To predict the entry-level name of a target object~$o$, the classifier, a multi-layer neural network, is fed the object's features, and applies softmax activation to the output layer that corresponds to the target vocabulary.

@@

Table \ref{tab:exp_VGvsMN} shows the accuracy of the models on the \mn test data.
%\footnote{ResNet$_{\text{VGMN}}$ with MN is comparable to its counterpart.}. 
We compare model effectiveness on predicting the entry-level name (column MN) against predicting the VG name . 
%We therefore consider an object's VG name less likely to represent the entry-level name than its MN name.

% and furthermore report results on the test instances where the two names differ (block VG$\neq$MN). 
%Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively.  
%We therefore consider an object's VG name less likely to represent the entry-level name than its MN name. 
% \gbt{add motivation for the latter, and make sure we address this when we discuss results; else, remove.}. 
%\cs{Left as items for the sake of a better overview for now}
\begin{table}[t]
	\centering
	\small
	\begin{tabular}{@{~}l@{~}|@{~}c@{~}|cc@{~}}
		\toprule
		&  & \multicolumn{2}{c}{GTtest} \\
		Model$_{\text{Vocab}}$ &  GTtrain &  VG & MN  \\ 
		\midrule
		FRCNN$_{\text{MN442}}$ & VG &  65.4 &      71.2   \\
		FRCNN$_{\text{VG1600}}$ & VG &    67.3 &      {\bf 74.5} \\
		\midrule \midrule
		\multicolumn{4}{c}{Classifiers: Transfer learning on MN}\\
		Features$_{\text{Vocab}}$ &   \\
		\midrule 
		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN &    {\bf 70.8} &      {\bf 80.6}  \\ 
		\midrule
		%ResNet$_{\text{VGMN}}$ & MN  & 60.9 &  68.6   \\

@@

A pervasive trend is that all models perform better 
at predicting the entry-level name (MN) than the VG name (VG), regardless of which vocabulary (Vocab) and which ground-truth (GTtrain) they are trained on. 
Note that the VG names were derived on the basis of 1-2 annotations per object, which, as shown in Section~\ref{sect:mn_analysis}, is not enough to robustly estimate entry-level names.
%even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively. 
The results therefore indicate that, even when not trained to do so (FRCNN$_{\text{VG1600}}$), models tend to predict entry-level names.
This is likely because entry-level names better reflect generalizations across objects.
% the FRCNN detection models do learn entry-level naming, with an accuracy of up to~$74.5$\%.

The overall best model is FRCNN$_\text{VG1600}$$_\text{-VGMN}$ (the transfer learning classifier with FRCNN$_\text{VG1600}$ features, trained on the \mn).
Fine-tuning on entry-level names also helps in the original task of predicting VG names, as FRCNN$_\text{VG1600}$$_\text{-VGMN}$ also improves in the VG evaluation (70.8\% accuracy, vs.\ \ 67.3\% without fine-tuning).
As expected, the classifiers using ResNet features obtain the worst results, but are still remarkably effective considering that they were trained on a fraction of FRCNN's training size using a simple transfer learning classifier.
%, in contrast to the fully-fledged CNN architecture of the FRCNN object detectors, the drop in effectiveness on entry-level naming (column MN, GTtrain MN) is decently low. 
%This confirms what we observed on the FRCNN results.

In sum, we find that models learn entry-level naming even when being trained on \arbitrary naming data, obtaining better results on entry-level prediction than VG name prediction for the same instances, and that they benefit from transfer learning with entry-level names. Instead, restricting the training vocabulary to entry-level names is not effective (all MN422 models are worse or comparable to VGMN/VG1600 models).
% Comparing the target vocabulary, MN442 and VG1600/VGMN, we see that the restriction on a smaller, but empirically derived vocabulary of entry-level names only, is not beneficial, with all MN442 models being worse or comparable to VGMN/VG100.

@@

%To date, little research has been done on how to finetune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, for purposes of \lv.
As Section~\ref{sec:manynames} showed, object naming is a linguistically complex phenomenon which exhibits a fair amount of agreement and also variation and potential errors.
Hence, it is striking that even models that are trained on \arbitrary names capture entry-level naming to a good extent.
However, our results also suggest that current \textit{evaluation} methods might not be very reliable when applied on \arbitrary names, probably punishing models for `errors' that actually constitute plausible alternatives.
The next section elaborates on this and proposes a fairer assessment of naming quality.

>>>>

\paragraph{Data}
We split \mn into training ($21$K objects) and test data ($1,072$), where the test data corresponds to the overlap of \mn (MN) and the \vg (VG) test split used by  \newcite{anderson2018updown}. 
The target vocabulary of the test data is MN442: the $442$~entry-level names we derived from \mnshort. %the overlap of MN442 and VG ($355$ names). 
For transfer learning we train models on the ground truth entry-level names provided by \mnshort, and compare this to training on \vgshort labels.

@@

\begin{itemize}
\item FRCNN$_{\text{VG1600}}$: We use \citeauthor{anderson2018updown}'s  \shortcite{anderson2018updown} model\footnote{We used the code and model available at  \url{github.com/peteanderson80/bottom-up-attention}. The model is trained with an additional output over attributes, but we only use the object class prediction layer.} that is optimized for a set of $1600$~object names in \vgshort. This set was obtained by first taking the $2500$~most frequent names in \vgshort and then (manually) filtering certain names.
 \item  FRCNN$_{\text{MN442}}$: We pre-process the \vgshort data as in \citeauthor{anderson2018updown}, but restrict the object classes to the $442$~entry-level names found in \mn (Section~\ref{sect:mn_analysis}). 
For training, we use a PyTorch reimplementation of Faster R-CNN\footnote{\url{github.com/jwyang/faster-rcnn.pytorch}}
\end{itemize}

The two former models are trained on \vg, which has almost $4$~million labeled objects.
\mn is too small to train object detection models on it from scratch, which requires learning millions of parameters.
On the other hand, obtaining enough naming data to be able to estimate entry-level names for larger datasets is very costly and probably unrealistic.
Therefore, we investigate the possibility of obtaining effective entry-level naming models via transfer learning, fine-tuning existing models with \mn data.
We do so with the standard methodology of taking the last hidden layer of existing Computer Vision models as input, and train object classification models to predict entry-level names (MN442).

We experiment with two kinds of (transferred) input features, different training vocabularies (similar to the detection models above), as well as ground-truth names with which the  instances are annotated (provided by either \mnshort or \vgshort).
This yields the following $5$~transfer-learning-based naming models:
\begin{itemize}
\item FRCNN$_{\text{VG1600--VGMN}}$:
	This model extracts features from the object detection model FRCNN$_{\text{VG1600}}$\footnote{
	As experimental results will show, FRCNN$_{\text{VG1600}}$ is more effective than FRCNN$_{\text{MN442}}$, so we only use the former.
}. We expect these to be very good features for our task, as they have been obtained with the same task (object classification) and dataset (\vg).  For each object (i.e.,~bounding box) in \mn, we extract its activation features from FRCNN's last hidden layer before the output layer. The model uses the VGMN vocabulary (overlap of the full ManyNames vocabulary with VG).
  \item ResNet$_{\text{VGMN}}$: 
For comparison, we consider a much less informed input, namely the features from the ResNet-101 image classification model, that was used to initialize the FRCNN models above, and pretrained on ImageNet \cite{imagenet_cvpr09}. 
Results should of course be worse, and our aim is to assess the feasibility of using such generic object representations to obtain entry-level names. ResNet$_{\text{VGMN}}$ uses the VGMN vocabulary. It is optimized on VG or MN ground truth names respectively.
 \item  ResNet$_{\text{MN442}}$:
 A variant of ResNet$_{\text{VGMN}}$, that is trained with a vocabulary of $442$~entry-level names. It is optimized on VG or MN ground truth names respectively.
\end{itemize}
Note that these five models are optimized on the $21$K~objects in \mn. 
To predict the entry-level name of a target object~$o$, the classifier, a multi-layer neural network, is fed the object's features, and applies softmax activation to the output layer that corresponds to the target vocabulary.

@@

Table \ref{tab:exp_VGvsMN} shows the accuracy of the models on the \mn test data\footnote{ResNet$_{\text{VGMN}}$ with MN is comparable to its couterpart.}. 
We compare model effectiveness on predicting the entry-level name (column MN) against predicting the VG name. 
%We therefore consider an object's VG name less likely to represent the entry-level name than its MN name.

% and furthermore report results on the test instances where the two names differ (block VG$\neq$MN). 
%Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively.  
%We therefore consider an object's VG name less likely to represent the entry-level name than its MN name. 
% \gbt{add motivation for the latter, and make sure we address this when we discuss results; else, remove.}. 
%\cs{Left as items for the sake of a better overview for now}

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{@{~}l@{~}|@{~}c@{~}|cc@{~}}
		\toprule
		&  & \multicolumn{2}{c}{GTtest} \\
		Model$_{\text{Vocab}}$ &  GTtrain &  VG & MN  \\ 
		\midrule
		FRCNN$_{\text{MN442}}$ & VG &  65.4 &      71.2   \\
		FRCNN$_{\text{VG1600}}$ & VG &    67.3 &      \textbf{74.5} \\
		\midrule \midrule
		\multicolumn{4}{c}{Classifiers: Transfer learning on MN}\\
		Features$_{\text{Vocab}}$ &   \\
		\midrule 
		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN &    \textbf{70.8} &      \textbf{80.6}  \\ 
		\midrule
		%ResNet$_{\text{VGMN}}$ & MN  & 60.9 &  68.6   \\

@@

A pervasive trend is that all models perform better 
at predicting the entry-level name (MN) than the VG name (VG), regardless of which vocabulary (Vocab) and which ground-truth (GTtrain) they were trained on.  
Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, is not enough to robustly estimate entry-level names. 
%, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively. 
%The results therefore indicate that, even when not trained to do so (FRCNN$_{\text{VG1600}}$), models tend to predict entry-level names.
The results therefore indicate that the even the FRCNN detection models do learn entry-level naming, despite not trained being to do so, with an accuracy of up to~$74.5$\%.

 The overall best model is FRCNN$_\text{VG1600}$$_\text{-VGMN}$ (the Vanilla classifier with FRCNN$_\text{VG1600}$ features, trained on  \mn). 
 Transfer-learning on entry-level names also helps in the original task of predicting VG names---FRCNN$_\text{VG1600}$$_\text{-VGMN}$ also improves in the VG evaluation ($70.8\%$~accuracy, vs.~$67.3\%$).
 % [CS] we need to do stat. significance tests
 %
As expected, the classifiers using ResNet features are the least effective, but considering that they were trained on a fraction of FRCNN's training size using a simple Vanilla classifier, in contrast to a fully-fledged CNN architecture of the FRCNN object detectors, the drop in effectiveness on entry-level naming (column MN, GTtrain MN) is decently low. 
%This confirms what we observed on the FRCNN results. 
%
In sum, we find that models learn entry-level naming when being trained on \arbitrary naming data, obtaining better results on entry-level prediction than VG name prediction for the same instances, and that they benefit from being trained on entry-levels using transfer learning. Comparing the target vocabulary, MN442 and VG1600/VGMN, we see that the restriction on a smaller, but empirically derived vocabulary of entry-level names only, is not beneficial, with all MN442 models being worse or comparable to VGMN/VG100.

@@

%To date, little research has been done on how to finetune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, for purposes of \lv.
As Section~\ref{sec:manynames} showed, object naming is a linguistically complex phenomenon which exhibits a fair amount of agreement and also variation and potential errors. 
Hence, it is striking that even models that are trained on (a lot of) \arbitrary names capture entry-level naming to a good extent.
However, our results also suggest that current \textit{evaluation} methods might not be very reliable when applied on \arbitrary names, probably punishing models for `errors' that actually constitute plausible alternatives.
The next section elaborates on this and proposes a fairer assessment of naming quality.

### 2020-02-05 papers/ACL2020/related.tex

Our approach is closer in this regard to \citet{zarriess-schlangen:2017}, who train an object naming model from names produced in referring expressions for real-world objects.
However, they do not have access to name annotations from (many) different annotators, whereas the additional annotations we collect enable more fine-grained evaluation.
The \mn dataset on which we rely is akin in spirit to older picture naming datasets (e.g.,~\citealt{rossion2004revisiting}) but focuses on naturalistic images of real-world objects instead of prototypical line drawings.

@@

In Computer Vision a major focus is visual object recognition, with object classification being a core task. 
Neural image classification systems are trained to label the most salient object in an image and often use the ImageNet \cite{imagenet_cvpr09} benchmark that labels images/objects with 1,000 fine-grained classes \cite{googlenet,he2016deep}. 
These neural classifiers have proven extremely useful %% SHORTENING %%in a large range of transfer learning scenarios. They are commonly used 
as pre-trained feature extractors in object detection systems that localize objects and predict their labels \cite{fasterrcnn2015}.
For instance, a commonly used object detector in \lv is \citet{anderson2018updown}'s so-called bottom-up model, which is based on a pre-trained ResNet classifier and fine-tuned Faster-RCNN \cite{fasterrcnn2015} for object detection and classification on \vg. 
We will use pre-trained ResNet and Faster-RCNN as models in this paper, extending and testing them for entry-level object naming.

\paragraph{The ManyNames Dataset}
The \mn dataset (MN, Anonymous, under review), which builds upon object annotations in VisualGenome (VG), provides up to 36 name annotations for 25K objects in images, see e.g.\ Figure \ref{fig:duck}.
The large number of name annotations per object in \mn gives us a way to reliably derive entry-level names, defined as the most frequent name for an object instance.
Its total vocabulary of names has 7,970 types; restricted to entry-level names, it has 442 types (still covering over 50\% of the object instances in \vg).
	%% SHORTENING %%The vocabulary of all entry-level names in \mn contains 442 types (the vocabulary of all names is 7970), covering more than 50\% of the objects in \vg, i.e. almost 2M objects in \vg are mentioned in region descriptions with one of these 442 entry-level names.
That these objects are diverse and visually situated in real-world scenes aligns with our view that entry-level names should be characterized at an instance-level, not at the class-level.
However, our manual inspection of the \mn data revealed a range of annotation problems, e.g., annotators occasionally named an object different from the one highlighted by the bounding box, or the right object but with an incorrect name (see Figure~\ref{fig:mistakes}, {\it error-box} and {\it error-visual}).
Although these errors are interesting human data, many of them would not occur in actual language use but are artifacts of the crowdsourcing methodology that uses simple graphical boxes to point workers to the annotation target.
%used for \mn, where there is a financial incentive to complete the task as quickly as possible.
As such, they pose challenges for our research goal, which is to see whether the object-naming ability of computational models resembles that of actual language users.
To overcome these, we collected a new layer of verification annotations on top of \mn, as follows.

>>>>

Our approach is closer in this regard to \citet{zarriess-schlangen:2017}, who train an object naming model from names produced in referring expressions for real-world objects.
However, they do not have access to name annotations from (many) different annotators, and rely on simple evaluation measures, whereas the additional annotations we collect enable more fine-grained evaluation.
The \mn dataset on which we rely is akin in spirit to older picture naming datasets (e.g.,~\citealt{rossion2004revisiting}) but focuses on naturalistic images of real-world objects instead of prototypical line drawings.

@@

In Computer Vision a major focus is visual object recognition, with object classification being a core task. 
Neural image classification systems are trained to label the most salient object in an image and often use the ImageNet \cite{imagenet_cvpr09} benchmark that labels images/objects with 1,000 fine-grained classes \cite{googlenet,he2016deep}. 
These neural classifiers have proven extremely useful %% SHORTENING %%in a large range of transfer learning scenarios. They are commonly used 
as pre-trained feature extractors in object detection systems that localize objects and predict their labels \cite{fasterrcnn2015}.
For instance, a commonly used object detector in \lv is \citeauthor{anderson2018updown}'s~(\citeyear{anderson2018updown}) so-called bottom-up model, which is based on a pre-trained ResNet classifier and fine-tuned Faster-RCNN \cite{fasterrcnn2015} for object detection and classification on \vg. 
We will use pre-trained ResNet and Faster-RCNN as models in this paper, extending and testing them for entry-level object naming.

\paragraph{The ManyNames Dataset}
The \mn dataset (MN, Anonymous, under review), which builds upon object annotations in VisualGenome (VG), provides up to $36$~name annotations for $25$K objects in images, see e.g.\ Figure \ref{fig:duck}.
The large number of name annotations per object in \mnshort gives us a way to reliably derive entry-level names, defined as the most frequent name for an object instance.
Its total vocabulary of names has $7,970$~types; restricted to entry-level names, it has $442$~types (still covering over $50\%$~of the  instances in \vgshort).
	%% SHORTENING %%The vocabulary of all entry-level names in \mn contains 442 types (the vocabulary of all names is 7970), covering more than 50\% of the objects in \vg, i.e. almost 2M objects in \vg are mentioned in region descriptions with one of these 442 entry-level names.
That these objects are diverse and visually situated in real-world scenes aligns with our view that entry-level names should be characterized at an instance-level, not at the class-level.
However, our manual inspection of the \mn data revealed a range of annotation problems, e.g., annotators occasionally named an object different from the one highlighted by the bounding box, or the right object but with an incorrect name (see Figure~\ref{fig:mistakes}, {\it error-box} and {\it error-visual}).
Although these errors are interesting human data, many of them would not occur in actual language use but are artifacts of the crowdsourcing methodology that uses simple graphical boxes to point workers to the annotation target.
%used for \mn, where there is a financial incentive to complete the task as quickly as possible.
As such, they pose challenges for our research goal, which is to see whether the object-naming ability of computational models resembles that of actual language users.
To overcome these, we collected a new layer of verification annotations on top of \mn, as follows.
